---
title: "EAS648_Lab1_Fei"
author: "Feixue Qi"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(ggplot2)
library(sf)
library(tidyverse)
library(sf)
library(ggspatial)
library(viridisLite)
library(viridis)
library(tmap)
```
```{r}
boulder <- st_read("C:/Users/qifei/OneDrive/桌面/EAS 648/EAS648_fei/input/Boulder_Data-20231025T203913Z-001/Boulder_Data/BoulderSocialMedia.shp")
boulder
```
```{r}
ggplot() +
    geom_sf(data =boulder,
    fill = NA, alpha = .2) +
    theme_bw()
```


```{r}
# change projection
boulder = st_transform(boulder, 26753) 
ggplot() +
    geom_sf(data =boulder,
    fill = NA, alpha = .2) +
    theme_bw()
```


```{r}
boulder %>%
    mutate(high_elev = ifelse(PT_Elev >= 2200, TRUE, FALSE))%>% 
ggplot() +
  geom_sf(aes(color=high_elev),
    fill = NA, alpha = .2)  +  
  theme_bw()
```


The map shows the location that elevation higher than 2200 meters is concentrated on south-west of Boulder Colorado. 




```{r}

## Add the data - these are specific to the vector or raster
tm_shape(boulder) + 
  ## which variable, is there a class interval, palette, and other options
  tm_symbols(col='NatMrk_Dis', 
             style='quantile', 
             palette = 'YlOrRd',
             border.lwd = NA,
             size = 0.1)
```


The map shows distance between photo taken location and natural landmarks in Boulder Colorado. It helps identify popular viewpoints or vantage points from which these photos were captured.This information can be valuable for tourists and nature enthusiasts looking to explore and photograph these areas, as it highlights specific locations that offer picturesque views of the natural landmarks.


```{r}
boulder %>%
  filter(DB ==  'Pano' | DB == 'Flickr') %>%
  ggplot(aes(x=DB, y=NatMrk_Dis)) + 
  geom_boxplot()
```


The figure shows using a box plot to compare mean distance of these photographs from the natural landmarks. There is no significant difference of photos between Flickr and Panramio.




